\Large \bf FlexAlloc: Dynamic Memory Partitioning\\ between the Corevisor and Hostvisor in SeKVM

### 2023-12-24 paper.tex
fixed format issues

Although the metadata structs have a much smaller memory footprint than the stage-2 page tables,
we designed and partially implemented a fully generalized dynamic allocation interface that
could be used to support dynamic allocation for all metadata structs which we call the
Dynamic Page Manager (DPM). DPM handles all of the work required to receive and return
memory from the hostvisor allowing other "services" in EL2 to exchange memory with DPM using
a very similiar interface to the \textit{alloc\\_pages} and \textit{free\\_pages} interface available in EL1. We describe
this interface in detail in Section 4.

>>>>

Although the metadata structs have a much smaller memory footprint than the stage-2 page tables,
we designed and partially implemented a fully generalized dynamic allocation interface that
could be used to support dynamic allocation for all metadata structs which we call the
Dynamic Page Manager (DPM). DPM handles all of the work required to receive and return
memory from the hostvisor allowing other "services" in EL2 to exchange memory with DPM using
a very similiar interface to the \textit{alloc\_pages} and \textit{free\_pages} interface available in EL1. We describe
this interface in detail in Section 4.
